% Phil Adams Resume
% Using LaTEX package 'moderncv'

\documentclass[11pt,letterpaper,final,sorting=ydnt]{moderncv}

% moderncv themes
\moderncvtheme[grey]{classic} % blue, orange, red, green, grey, roman
%\moderncvtheme[green]{casual} % blue, orange, red, green, grey, roman
\moderncvicons{awesome}

% fonts...
\usepackage{lmodern}
\renewcommand{\familydefault}{\sfdefault}  % sans serif as default

% character encoding
%\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths} % required when changes are made to page layout lengths

%\usepackage[backend=biber,
%            style=authoryear,
%            url=false,
%            isbn=false,
%            doi=false,
%            backref=true,
%            maxcitenames=20]{biblatex}
%\addbibresource{publications.bib}

% personal data
\firstname{Phil}
\familyname{Adams}
% \title{}
\address{102 North Baker}{Ithaca NY 14853}
% \phone{(610) 613 0153}
% \fax{fax (optional)}
\mobile{(412) 440-7445}
\email{philadams.net@gmail.com}
% \extrainfo{pja22@cs.cornell.edu}
% \photo[64pt]{picture}
% \quote{Some quote (optional)}
%\nopagenumbers{}

\begin{document}
\maketitle

\section{Education}
\cventry{2010--}{PhD in Information Science}{Cornell University}{Ithaca NY}{}{Advisor: Geri Gay; Committee: Tanzeem Choudhury, Elaine Wethington\\Concentration: Human-Computer Interaction; Minor: Human Development}
\cventry{2010--2013}{Master of Science in Information Science}{Cornell University}{Ithaca NY}{}{}
\cventry{2009--2010}{Master of Engineering in Computer Science}{Cornell University}{Ithaca NY}{}{}
\cventry{2005--2009}{Bachelor of Arts in Information Science}{Cornell University}{Ithaca NY}{}{}

\section{Experience}
\cventry{2008--Present}{Research Assistant}{Cornell University Information
Science}{Ithaca NY}{}{Working with Geri Gay, Tanzeem Choudhury, Elaine
Wethington, Deborah Estrin, and others to better understand the role of mobile
technologies in persuasive health.  Focusing on using mobile applications to
improve quality of life and wellbeing as part of the Mobile Health team.}
\cventry{Summer 2014}{User Experience Research Intern}{Google}{Mountain View
CA}{}{Working with Zuiena Kabir and Jhilmil Jain on the Android User Experience
Research team at Google, I conducted research into user behavior on mobile
devices.}
\cventry{Summer 2013}{User Experience Research Intern}{Google}{Mountain View
CA}{}{Working with Mike Brzozowski and Laura Granka on the Google+ User
Experience Research team at Google, I conducted research into how users join
and participate in Google+ Communities.}
\cventry{2009--2015}{Graduate Resident Fellow}{Cornell University}{Ithaca
NY}{}{Serving as an academic and social mentor to undergraduate students as a
Fellow in Cornell's living-learning community initiative. Roles include
fostering leadership and agency; connecting residents with faculty and research
opportunities; hosting campus guests; and coordinating a variety of academic
and social trips and activities.}
\cventry{2014--2015}{Graduate Teaching Fellow}{Cornell University}{Ithaca
NY}{}{The Graduate Teaching Assistant Fellowship is a program of Cornell
University's Center for Teaching Excellence. Fellows are select graduate
students who design and implement teaching programs, events, and resources that
foster teaching excellence and innovative pedagogical practice across campus.}
\cventry{2006--2010}{Teaching Assistant}{Cornell University}{Ithaca
NY}{}{Developing and teaching section material for CS/INFO 1300 \emph{Web
usability and design} \emph{Web programming}, CS/INFO 2300 \emph{Servers and
databases} in both undergraduate and graduate capacities. I continue to guest
lecture on special topics and in professors' absence in these and other
courses, including INFO 4400/6400 \emph{Advanced Human-Computer Interaction}
and INFO 6130 \emph{Health and Computation}.}
\cventry{1999--2010}{Business Intern}{World Cup Sports Academy}{Devon
PA}{}{Myriad of responsibilities, including: coaching soccer players ages 4-18
at all levels, in addition to one season coaching a high school JV squad;
directing camp operations, often leading a team of highschool teachers and
college/highschool students; overseeing marketing campaigns and fostering
client relationships; building company website (wcupsa.com); developing new
programs.}
\cventry{2006--2008}{Web Application Developer}{CIT Systems Management}{Ithaca
NY}{}{Developing and maintaining web-based applications in support of the
services provided by Cornell Information Technologies. Left CIT in 2008 to
focus on research opportunities.}
%\cventry{Fall 2007}{Research Assistant}{Cornell e-Rulemaking
%Initiative}{Ithaca NY}{}{Developing interactive interfaces for the Public
%Interface Project, working to improve the usability and functionality of
%regulations.gov.}
\cventry{2004--2010}{Freelance Web Developer}{philadams.net}{Ithaca
NY}{}{Clients include businesses, charitable organizations, and university
student groups.}

\section{Professional Leadership and Service}
\cventry{2013--Present}{Co-coordinator}{Information Science Graduate Seminar Series}{Ithaca NY}{}{Organizing and hosting speakers and panels. \url{http://infosci.cornell.edu/graduate-seminar-series}}
\cventry{2011--2014}{Graduate Representative}{Information Science Curriculum
Committee}{Ithaca NY}{}{The committee designs and maintains degree requirements
and courses in the curriculum, and oversees various other issues related to the
program. Served as the undergraduate representative 2007-08.}
\cventry{2014--Present}{Graduate Representative}{Gates Hall Space Use Committee}{Ithaca NY}{}{}
\cventry{2011--Present}{Conference Reviewer}{}{}{}{Reviewer for paper submissions at CHI 2012-2015 and CSCW 2013-2014.}
\cventry{2014}{Conference Student Volunteer}{}{}{}{CHI 2014 (Toronto), CSCW 2014 (Baltimore).}
%\cventry{2010--Present}{Member}{Association for Computing Machinery (ACM)}{}{}{}
\cventry{2007--2009}{Co-founder and President}{Cornell Web Club}{Ithaca NY}{}{}

\section{Relevant Awards}
\cventry{2011}{Graduate Research Fellow}{National Science Foundation}{}{}{The
National Science Foundation's Graduate Research Fellowship Program helps ensure
the vitality of the human resource base of science and engineering in the
United States and reinforces its diversity, recognizing and supporting
outstanding graduate students in NSF-supported science, technology,
engineering, and mathematics disciplines. The award provides funding for 3
years of graduate study.}
\cventry{2009}{Inductee}{Phi Beta Kappa}{}{}{}

%\section{Service}
%\cventry{2005}{Volunteer}{Love in Action}{Masaka, Uganda}{}{Helped develop an
%internet caf\'e providing services to doctors, teachers, students, lawyers,
%aid workers, and the general population. Established NGO status for Love in
%Action. Mentored at an AIDS orphanage. Four months on-site, with continued
%involvement in raising awareness and funding.}
%\cventry{2005}{Volunteer}{ASODECAH}{La Flor, Costa Rica}{}{Member of the volunteer work program of the Association for the Development of Environmental and Human Consciousness (ASODECAH) for six weeks. Responsibilities included various projects in rain forest regeneration and agro-ecological farming. ASODECAH demonstrates practical, sustainable management of land resources, provides work for the community, and educates locals and visitors about the environment.}

%\section{Languages}
%\cvlanguage{Spanish}{Intermediate}{Spoken and written}

\section{Computer Languages and Frameworks}
\cvline{}{\small Python, Android/Java, Javascript, R, HTML5/CSS, PHP}

% publications from publications.bib
% figure out a way of styling this to use biber???
%\printbibliography[title=Publications,]
\nocite{*}
\bibliographystyle{unsrt}
\bibliography{publications}

%\emph{\\References available on request.}

\end{document}

% TODO: add leadership course??
